\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fontenc}
\usepackage{parskip}
\usepackage{xcolor}

% Colors
\definecolor{headingblue}{HTML}{1A5276}
\definecolor{rulecolor}{HTML}{2C3E50}
\definecolor{linkblue}{HTML}{2471A3}
\definecolor{subtlegray}{HTML}{555555}

% Section formatting
\titleformat{\section}{\large\bfseries\color{headingblue}}{}{0em}{}[\color{rulecolor}\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\pagestyle{empty}
\setlist[itemize]{nosep, left=0pt, labelsep=5pt, itemsep=1pt}

\begin{document}

% Header
\begin{center}
{\LARGE\bfseries Mandla Mathebula}\\[3pt]
+27 79 774 9367 \enspace|\enspace mathebulam000@gmail.com \enspace|\enspace Cape Town, South Africa\\[2pt]
\href{https://linkedin.com/in/mandla-mathebula-4258a518a}{\color{linkblue}LinkedIn} \enspace|\enspace \href{https://github.com/mamathebula}{\color{linkblue}GitHub} \enspace|\enspace \href{https://applyza.co.za/resume_mandla/}{\color{linkblue}Portfolio}
\end{center}

% Professional Summary
\section{Professional Summary}
Cloud Support Engineer with 4+ years of experience delivering automation, reliability, and operational improvements across AWS and Azure environments. Promoted from L4 to L5 within 21 months at Amazon Web Services for driving high-impact automation initiatives and improving operational efficiency. Proven track record of reducing latency, improving SLA performance, and implementing scalable serverless solutions that drive cost savings and operational excellence.

% Technical Skills
\section{Technical Skills}
\textbf{Cloud Platforms:} AWS (EC2, Lambda, S3, API Gateway, CloudFormation, CloudWatch, IAM, SNS, EventBridge, VPC, EBS), Microsoft Azure\\
\textbf{Infrastructure \& DevOps:} Infrastructure as Code (CloudFormation), CI/CD Pipelines, GitHub Actions, Linux, Serverless Architecture, Deployment Automation\\
\textbf{Programming \& Automation:} Python, JavaScript, Bash, REST APIs, Automation Scripting\\
\textbf{Monitoring \& Operations:} CloudWatch, Grafana, Alerta, Observability, Incident Management, Root Cause Analysis, SLA Management\\
\textbf{Security \& Compliance:} IAM Policies, SCPs, Identity and Access Management, Cloud Security Best Practices\\
\textbf{Architecture \& Methodologies:} Serverless Architecture, Scalable Systems Design, Cloud Lifecycle Management, Agile, UAT

% Professional Experience
\section{Professional Experience}

\textbf{Senior Cloud Support Engineer} \hfill \textbf{June 2024 -- Present}\\
\textit{Amazon Web Services}
\begin{itemize}
  \item Served as subject matter expert for AWS Marketplace products including Single AMI and CloudFormation-based deployments.
  \item Led user acceptance testing sessions and delivered operational reporting used by leadership to improve team efficiency.
  \item Engineered automation for architecture diagram reviews using AI tooling, reducing processing time by 92\% (2 hours to under 10 minutes) and improving SLA performance by 75\%.
  \item Designed a JavaScript automation framework integrating 40+ internal systems to streamline operational workflows.
  \item Built a Python serverless automation solution using AWS Lambda, SNS, and CloudWatch to manage infrastructure lifecycle and enforce tagging policies.
  \item Mentored engineers to operational independence and contributed to cross-team knowledge sharing initiatives.
  \item Led a hackathon-winning GenAI project that generated automated case summaries within Salesforce, saving 5--10 minutes per case and delivering 8--16 hours of team productivity gains daily.
  \item Contributed to the launch of AWS License Manager enhancements enabling Red Hat subscription switching without instance redeployment across regions.
\end{itemize}

\textbf{Cloud Engineer} \hfill \textbf{June 2023 -- May 2024}\\
\textit{Momentum Metropolitan Holdings}
\begin{itemize}
  \item Provided technical support for AWS and Azure environments across 150+ cloud accounts.
  \item Served as primary technical contact for cloud infrastructure troubleshooting and operational incidents.
  \item Managed escalations with vendor support teams including AWS and Microsoft.
  \item Monitored cloud infrastructure for performance, availability, and cost optimization opportunities.
  \item Implemented cloud security and compliance configurations aligned with industry best practices.
  \item Developed automation solutions to improve operational efficiency and reduce manual workload.
  \item Collaborated with DevOps engineers, Solutions Architects, and account managers to improve service delivery.
\end{itemize}



\textbf{Branch VIP Support Engineer} \hfill \textbf{June 2021 -- May 2023}\\
\textit{Momentum Metropolitan Holdings}
\begin{itemize}
  \item Delivered high-priority IT support for executive and VIP users across enterprise environments.
  \item Performed root cause analysis, incident management, and service request fulfillment.
  \item Communicated critical system updates and escalations to senior management.
  \item Provided remote standby support and ensured minimal operational disruption during incidents.
\end{itemize}

\textbf{IT Support Engineer (Internship)} \hfill \textbf{November 2020 -- May 2021}\\
\textit{Momentum Metropolitan Holdings}
\begin{itemize}
  \item Provided on-site and remote technical support for hardware, software, and network issues.
  \item Assisted with enterprise system migrations including workstation imaging, VPN configuration, and productivity tool deployments.
  \item Supported large-scale migration projects across multiple branches including workstation setup and collaboration tool configuration.
\end{itemize}

% Projects
\section{Projects}

\href{https://github.com/mamathebula/ebs-volume-migration}{\color{linkblue}\textbf{EBS Volume Migration Tool (gp2 $\rightarrow$ gp3)}} \enspace|\enspace \textit{Bash, AWS CLI, EC2 API}\\
Automated migration of 200+ EBS volumes across regions. Achieved 20\% cost reduction and \$4,000+ annual savings with zero downtime.

\href{https://github.com/mamathebula/security-group-monitor}{\color{linkblue}\textbf{Security Group Monitor}} \enspace|\enspace \textit{Python, Lambda, CloudFormation, EventBridge, SNS}\\
Serverless security monitoring detecting open security group rules in real time. Automatic rule revocation with alerting and tag-based whitelisting. Near-instant compliance enforcement.

\href{https://github.com/mamathebula/lambda-runtime-updater}{\color{linkblue}\textbf{Lambda Runtime Bulk Updater}} \enspace|\enspace \textit{Bash, AWS CLI, Lambda API}\\
Automated runtime updates for 100+ Lambda functions simultaneously. Reduced full-day manual operation to under 5 minutes using parallel processing.

\href{https://github.com/mamathebula/aws-resource-cleanup}{\color{linkblue}\textbf{AWS Resource Cleanup Stack}} \enspace|\enspace \textit{CloudFormation, Lambda, EventBridge, SNS}\\
Automated lifecycle management for unused AWS resources. Cleaned up 500+ unused volumes and snapshots, saving \$1,500+ annually.

\href{https://applyza.co.za/resume_mandla/}{\color{linkblue}\textbf{Professional Portfolio \& CI/CD Pipeline}} \enspace|\enspace \textit{React, GitHub Actions, Cloudflare Pages}\\
Developer portfolio with automated CI/CD. GitHub push-triggered builds and production deployment through global edge network.

% Education
\section{Education}
\textbf{Tshwane University of Technology} \hfill \textbf{Completed: 2022}\\
National Diploma in Information Technology --- Intelligent Industrial Systems

% Certifications
\section{Certifications}
\begin{itemize}
  \item AWS Certified Cloud Practitioner (2023)
  \item Microsoft Cybersecurity Architect (SC-100)
  \item Microsoft Security, Compliance, and Identity Fundamentals (SC-900)
  \item Microsoft 365 Fundamentals (MS-900)
  \item Apple macOS Support Essentials --- Monterey
\end{itemize}

% Key Achievements
\section{Key Achievements}
\begin{itemize}
  \item Promoted from L4 to L5 within 21 months at Amazon Web Services.
  \item Won Q2 2025 GenAI Hackathon for developing an AI case summarization tool saving up to 16 hours daily team-wide.
  \item Reduced architecture review SLA from 48 hours to 12 hours through automation.
  \item Eliminated a 550+ case backlog in 3 days through automation and workflow optimization.
  \item Accelerated AWS Marketplace product listing time from 14 days to under 1 hour.
\end{itemize}

\end{document}
